\documentclass{standalone}
\usepackage{standalone}

\begin{document}

\chapter{Methodology}
This chapter describes our process to detect license plate given an input image, and separation of the individual numbers and character sequence from detected license plate. The input image may come from variety of sources. We have put on a validation method to detect if there is actually a license plate in the input image.

  \input{./tex/methods/implementation}
  \input{./tex/methods/overview}

\section{Plate Localization}
This stage contains a sequence of steps that enhance the plate like regions of an image and output an image that can be used directly for the next stage - plate detection.

  \input{./tex/methods/rescaling}
  \input{./tex/methods/grayscale}
  \input{./tex/methods/sobelEdges}
  \input{./tex/methods/gaussian}
  \input{./tex/methods/enhancement}
  \input{./tex/methods/matchedFilter}
  \input{./tex/methods/locatePlate}

\section{Plate Extraction}
This section describes the procedure to extract the license plate using the outputs from preprocessing stage. 
  \input{./tex/methods/cannyEdges}
  \input{./tex/methods/contourAnalysis}
  \input{./tex/methods/extraction}
  \input{./tex/methods/binary}
  \input{./tex/methods/denoising}

\input{./tex/methods/segmentation}


\section{Character Recognition}
The character recognition is the final and most crucial part of the automated system. Although we did not implement a system for recognition, we used tested various method and by following up \cite{joarder2012bangla}, we formulated simple feature extraction which will be useful in our future work. Although we did not implement it, but we provided our design and plan to implement a multilayer feed-forward neural network for character recognition.

  \input{./tex/methods/featureExtraction}
  \input{./tex/methods/neuralNet}

\end{document}