\documentclass{standalone}
\usepackage{standalone}

\begin{document}
\chapter{Background Study}

\section{Historical View}
As far as we know that ANPR system was first invented in 1976. It was done by the Police Scientific Development Branch in the UK. Industrial usage begun in 1979. But ANPR got more known in the 1990's for their cheap implementation from the previous costly systems. The first ANPR dataset was made in early 2000s. This system was used to solve a murder occurred in November 2005, in Bradford, UK, to locate and find the culprits behind the killing of Sharon Beshenivsky.

From that point forward tag acknowledgment has advanced and been utilized by police and different associations for various purposes and has turned out to be less expensive and speedier, yet not sufficiently shoddy for private utilize. In the following areas, a portion of the current techniques in the zone of tag location and acknowledgment will be talked about.

\section{Literature Review}
The first task was to find the problem domain to work on. The next task was to make literature reviews for our work plan and also for ensuring that we are not doing something again or worse. We've found few papers related to ALPR for Bengali languages and many more in different languages. Finally, we did select 24 papers to read and review for our thesis work. We've written 7 review papers those seemed close to our topic. From those papers and reviews we've managed to find and understand our particular domain of work which will be described in the later parts.
\end{document}